Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-20 src-latex/parts/20-related-work.tex
Avoid isolated lines
Comment redundant paragraph

In this study, we consider Tesseract version 4, Kraken and \peroocr.
They were selected because of their ease of use (in the case of Tesseract and Kraken)
or because of their performance (in the case of \peroocr),
but further work should include more systems from our initial selection.

@@

Based on those works, we chose to test three OCR systems, namely, Tesseract, Pero OCR, and Kraken. We also adopt two deep-learning-based French language models, available in packaged software libraries, already trained for the NER task and that we can adapt to the domain of historical directories: SpaCy NLP pipelines and CamemBERT.

@@

The Figure \ref{fig.pipeline} depicts the evaluation protocol used to assess the combined performance of these OCR and NER systems.

>>>>

% In this study, we consider Tesseract version 4, Kraken and \peroocr.
% They were selected because of their ease of use (in the case of Tesseract and Kraken)
% or because of their performance (in the case of \peroocr),
% but further work should include more systems from our initial selection.

@@

Based on those works, we chose to test three OCR systems, namely, Tesseract, Pero OCR, and Kraken. We also adopt two deep-learning-based French language models, available in packaged software libraries, already trained for the NER task and that we can adapt to the domain of historical directories: SpaCy NLP pipelines and CamemBERT.
\Cref{fig.pipeline} depicts the evaluation protocol used to assess the combined performance of these OCR and NER systems.

@@
